### 2012-04-18 trunk/ijcis-pos-model/sources/temporaldatabases.tex
update

\subsection{Understanding Valid-time Databases}
This subsection is devoted to describe the behaviour of a crisp valid-time database. For the shake of simplicity, only the three main operations in the Data Manipulation Language \emph{DML} a.k.a \emph{CRUD} (CReate Update, Delete) operations are shown. Usually the DML operations in a temporal database are re-defined e.g. a typical update sentence in SQL could be re-defined by means of several insert and update sentences. Therefore, in order to be clear, these high level primitives in the DML for a valid-time database are usually noted as Insert, Modify and Delete. In the following subsections each primitive is defined and explained. Finally a illustrative example is given. For a more complete information on the behaviour of a bitemporal database, please refer to ~\cite{Jensen1994}.

@@

\begin{definition}
\label{def:close-a-crisp-interval-r}
Consider two crisp intervals $I= \left[a ,b \right]$ and $J= \left[c ,d \right]$, $c > a$. The CloseR$\left(I, J\right)$ function allows to close the right-open interval $I$ with respect to the first value $d$ in $J$:
\begin{align}
\mbox{CloseR} \left( I, J \right) &=& \\ 
\begin{cases}
\nonumber
I & \mbox{ if } b \neq +\infty \\
I=\left[a, c \right[ & \mbox{ if } b = +\infty \wedge J > I
\end{cases}
\end{align}
\end{definition}

@@

\begin{eqnarray}
%\label{eq:close-current}
\text{Close-current} \left(R, A, J \right) =\\
\begin{cases}
\nonumber
\big \lbrace R - \left(A, I \right) \cup \left \lbrace \left(A, \mbox{ CloseR } \left(I, J\right) \right) \cup \left(A, J\right)\right \rbrace  \big \rbrace \\
\nonumber
\mbox{ if } I = \mbox{ Current } \left(R, A \right) \wedge J > \mbox{ CloseR } \left(I, J \right)   \\
\nonumber R , \text{ in any other case}
\end{cases}
\end{eqnarray}
\end{definition}

>>>>

\subsection{\label{subsubsec:Understanding-valid-time-databases}Understanding Valid-time Databases}
This subsection is devoted to describe the behaviour of a crisp valid-time database. For the shake of simplicity, only the three main operations in the Data Manipulation Language \emph{DML} a.k.a \emph{CRUD} (CReate Update, Delete) operations are shown. Usually the DML operations in a temporal database are re-defined e.g. a typical update sentence in SQL could be re-defined by means of several insert and update sentences. Therefore, in order to be clear, these high level primitives in the DML for a valid-time database are usually noted as Insert, Modify and Delete. In the following subsections each primitive is defined and explained. Finally a illustrative example is given. For a more complete information on the behaviour of a bitemporal database, please refer to ~\cite{Jensen1994}.

@@

\begin{definition}
\label{def:close-a-crisp-interval-r}
Consider two crisp intervals $I= \left[a ,b \right]$ and $J= \left[c ,d \right]$, $c > a$. The CloseR$\left(I, J\right)$ function allows to close the right-open interval $I$ with respect to the first value $d$ in $J$:
\begin{align}
\label{eq:close-a-crisp-interval}
\mbox{CloseR} \left( I, J \right) &=& \\ 
\begin{cases}
\nonumber
I & \mbox{ if } b \neq +\infty \\
I=\left[a, c \right[ & \mbox{ if } b = +\infty \wedge J > I
\end{cases}
\end{align}
\end{definition}

@@

\begin{eqnarray}
\label{eq:close-current}
\text{Close-current} \left(R, A, J \right) =\\
\begin{cases}
\nonumber
\big \lbrace R - \left(A, I \right) \cup \left \lbrace \left(A, \mbox{ CloseR } \left(I, J\right) \right) \cup \left(A, J\right)\right \rbrace  \big \rbrace \\
\nonumber
\mbox{ if } I = \mbox{ Current } \left(R, A \right) \wedge J > \mbox{ CloseR } \left(I, J \right)   \\
\nonumber R , \text{ in any other case}
\end{cases}
\end{eqnarray}
\end{definition}
